\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Final Assignment: Integration of Tools and Practices}
\author{Your Name}
\date{\today}

\begin{document}

\maketitle
\tableofcontents

\section{Introduction}
This document contains the answers to the final assignment questions.

\section{Git and GitHub}
\subsection{Repository Initialization and Commits}
Write about how you set up the repository for this assignment. Explain every step in detail.

\subsection{GitHub Actions for LaTeX Compilation}
Provide a walkthrough of setting up GitHub Actions to automatically compile your LaTeX document and any challenges you encountered.

\section{Exploration Tasks}
\subsection{Vim Advanced Features}
Explore and document 3 advanced features of Vim that were not covered in class.

\subsection{Memory Profiling}
\subsubsection{Memory Leak}
In short, explain what memory leaks are and how they might happen in your program.

\subsubsection{Memory Profilers}
Read about a tool called Valgrind and write about its purpose and how it helps when memory leaks happen.

\subsection{GNU/Linux Bash Scripting}
\subsubsection{fzf}
Read about a handy CLI tool called fzf and answer the following questions:
\begin{itemize}
    \item What is fuzzy searching? Give a short description.
    \item Install fzf on your machine and give a description of what the following command does: \texttt{ls | fzf}
\end{itemize}

\subsubsection{Using fzf to find your favorite PDF}
Write a command to list the directory of all the files with the extension .PDF using \texttt{fd}. Then, write a command to use \texttt{fzf} to select a PDF from the data gathered.

\subsubsection{Opening the file using Zathura}
Write a command that uses the commands above to open the file using Zathura.

\section{Git and FOSS}
\subsection{README.md}
Make sure to include a basic README.md file in your GitHub repository that describes the aim of this repository and its purpose.

\subsection{Issues}
Create a sample issue in the repository below and attach its screenshot in your LaTeX document:
\url{https://github.com/Milikxe/CW-Final}

\subsection{FOSS contribution}
Do you see yourself contributing to FOSS projects in the future? If yes, what kind of projects are you interested in contributing to? If no, why not?

\end{document}
